---
title: "Lab2Q4"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading required libraries
```{r,message=F,warning=F}
library(dplyr)
library(ggplot2)
```

## Reading data
```{r}
data = read.csv("June 10-July 12, 2015 - Gaming, Jobs and Broadband - CSV.csv")
```

### Removing the variables having more than 65% missing values
```{r}
dt = data[, colMeans(is.na(data)) <= .65]
```

## Missing value imputation

We will replace the remaining missing values using Mode imputation

```{r}
Mode <- function(x, na.rm = FALSE) {
    if(na.rm){
        x = x[!is.na(x)]
    }
    
    ux <- unique(x)
    return(ux[which.max(tabulate(match(x, ux)))])
}

vec = c()
for(n in names(dt))
{
    s = sum(is.na(dt[,n]))
    if(s >0)
    {
        vec = c(vec,n)
    }
}

for(var in vec)
{
    dt[is.na(dt[,var]),var] <- Mode(dt[,var],na.rm = T)
}
```

## Converting selected variables to factor
```{r}
conames = c("int_date","age","zipcode","weight","standwt","ï..psraid")
dt[,!colnames(dt) %in% conames] = lapply(dt[,!colnames(dt) %in% conames], as.factor)
```

# How would you rate your community as a place to live?

Overall, how would you rate your community as a place to live? Would you say it is... 

1	Excellent

2	Good

3	Only fair, OR

4	Poor?

8	(VOL.) Don't know

9	(VOL.) Refused


## Creating data frame with useful variables
```{r}
q1 = select(dt,sample,lang,usr,cregion,state,form,sex,age,race,q1,marital,par,educ2,inc)
```
We will look at couple of graphs and variables to answer the above question

## Plot 1 : Age Distribution
```{r}
ggplot(q1, aes(x = age)) + geom_histogram(color = "black", fill = "red")
```

From the above plot, we can observe that most of the people belonging to age group 50-70 participated in survey.

## Plot 2 : q1 vs Race
```{r}
ggplot(q1,aes(race,fill = race)) +geom_bar()
```

From the frequency curve, we can see that most surveys are from people belonging to race group 1, i.e, White

```{r}
ggplot(q1,aes(q1,fill = race)) + geom_bar(position = "dodge")

```

From the above curve we can conclude that ppl belonging to "White"" race have voted the most for Excellent/Good quality of life,while the minority race such as Native American/American Indian have voted the least for Excellent/Good quality of life.

## Plot 3 : q1 vs Sex
```{r}
ggplot(q1,aes(q1,fill = sex)) + geom_bar(position = "dodge") + scale_fill_discrete(name="Sex",labels=c("Male", "Female"))
```

From the above plot,we can observe that more number of females have voted for "Excellent" quality while almost equal number of males and females have voted for "Good" quality.

## Plot 4 : q1 vs PAR
```{r}
ggplot(q1, aes(x = q1, fill = par)) + geom_bar(position = "dodge") + scale_fill_discrete(name = "parent/guardian of children under age 18", labels = c("Yes","No","Refused"))
```

Survey states that people or guardian who doesn't have children under age 18 have rated more to "Excellent/Good" community to live in.

# Q2 Part(a) : Do you ever play video games on a computer, TV, game console, or portable device like a cell phone? 

1	Yes

2	No

8	(VOL.) Don't know

9	(VOL.) Refused



```{r}
Q2 <- select(dt,sample:q1,game1:game4,age,race,marital,par,educ2,inc)
Q2 <- select(Q2, -(sample:form))
Q2 <- select(Q2, -q1,-marital)
levels(Q2$game1)[4] = "8"
```

## Plot 1: game1 vs Parent
```{r}
ggplot(Q2, aes(x = game1, fill = par)) + geom_bar(position = "dodge") + scale_fill_discrete(name = "parent/guardian of children under age 18", labels = c("Yes","No","Refused"))

```

Survey states that people or guardian who doesn't have children under age 18 does not play video games.

# Q2 Part(b) : Video games are a waste of time

## Plot 2: game2b vs income
```{r}
ggplot(Q2,aes(x = game2b, fill = inc)) + geom_bar() + facet_grid(~inc) 

```

Most of the people believe that video games are waste of time is true for some of the games but not others,whereas people earning(30k-40k) believes that it is true for all games.


# Q2 Part(c) : Most people who play video games are men

## Plot 3: game3a vs sex
```{r}
ggplot(Q2, aes(x = game3a, fill = sex)) + geom_bar(position = "dodge") + scale_fill_discrete(name = "Sex", labels = c("Male","Female"))
```

Almost everyone has agreed that most people who play video games are men.

# Q2 Part(d) : People who play violent video games are more likely to be violent themselves

## Plot 4 : game3b vs race
```{r}
ggplot(Q2, aes(x = game3b, fill = race)) + geom_bar() + facet_grid(~race)
```

Survey states that a person from any race disagrees with the fact that b. People who play violent video games are more likely to be violent themselves.


# Q3 About how often do you use the internet?

About how often do you use the internet? [READ] {Modified Teens Relationships}

1	Almost constantly

2	Several times a day

3	About once a day

4	Several times a week, OR

5	Less often?

8	(VOL.) Don’t know

9	(VOL.) Refused


## Creating dataframe with useful variables
```{r}
Q3 = select(dt,sample,lang,usr,cregion,state,sex,par,educ2,race,inc,age,emplnw,intfreq)
```

We will merge levels of some factors that do not provide much information

```{r}
levels(Q3$intfreq)[7] = "8"
levels(Q3$intfreq)
levels(Q3$inc)[11] = "98"
```

We will be looking at couple of plots to draw inferences and relationship between internet frequency and other factors

## Plot 1 : intfreq
```{r}
table(Q3$intfreq)
ggplot(Q3,aes(intfreq)) + geom_bar(fill = "blue")
```

The above frequency tells us that majority of people voted for option 2 i.e. "Several times a day".

## Plot 2 : intfreq vs sex
```{r}
ggplot(Q3,aes(intfreq,fill = sex)) + geom_bar(position = "dodge") + scale_fill_discrete(name="Sex",labels=c("Male", "Female"))
```

From the above plot, we can see that males tend to spend more time on internet while there are more number of female users than male users.

## Plot 3 : intfreq vs parental
```{r}
ggplot(Q3,aes(intfreq,fill = par)) + geom_bar(position = "dodge") +scale_fill_discrete(name="Parental Status",labels=c("Yes", "No","Refused"))

```

From the above graph, we can observe that the people who are parent of under 18 year age tend to use internet comparatively less. 

## Plot 4 :intfreq vs age
```{r}
ggplot(Q3,aes(y=age,x=intfreq)) + geom_boxplot(aes(fill = intfreq)) + scale_fill_discrete(name="Internet Frequency", labels=c("Constantly", "Several","Once/day","Several times/week","Less Often","Refused"))

```

From the above plot,we can conclude that people belonging to younger age group(<40) tend to use internet more oftenly that others.

## Plot 5 : intfreq vs income
```{r}

levels(Q3$inc)[11] = "98"
ggplot(Q3,aes(x = intfreq,fill = inc)) + geom_bar() + facet_wrap(~inc)

```

By observing the above plots carefully,we came to know that as income level of people increases they tend to spend more time on internet.